Geometric variational problems

### 2020-11-08 NSF2020/Description/broaderimpacts.tex
pass through broader impacts file

\noindent
{\bf Shidong Jiang}: {\it NSF DMS-1418918,
  Efficient High-Order Parallel Algorithms for Large-Scale Photonics Simulation},
\$150,000, 08/15/2014 - 06/30/2017, PI.
{\it Intellectual merit:} The goal of the proposed research is to develop
\emph{robust, high-order numerical methods} and \emph{efficient parallel algorithms} to
achieve greater accuracy and larger scale for photonics simulation.

%Jiang, Kloeckner, and their collaborators have constructed
%a stable second kind integral equation formulation for the mode calculation of optical
%waveguides of arbitrary shape; they have quantified the effect of cladding thickness on
%modal confinement loss in photonic waveguides; they have developed high-quality software
%package for solving integral equations in both two and three dimensions.

\noindent
{\it Broader impacts:} 
During the funded period, the PI has published or submitted twelve papers to refereed international journals~\cite{jiang2014sisc,bao2015jcp,jiang2015acom,greengard2015jcp,fu2015pre,gan2016sisc,jiang2016jcp,jiang2016oe,ben2016tpm,jiang2017siammms,jiang2017cicp,lai2018acha},
and presented the research results at many institutions and international
conferences/workshops to disseminate research results. On the education side,
the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
and Szu-Pei Fu~\cite{fu2015pre,Fu2018_SIAM} (co-advised with Yuan-Nan Young),
with the partial support of the grant.
%Finally, the software package developed by both PIs of this collaborative grant
%has many applications in scientific computing, especially those related to
%the integral equation methods.

@@

\begin{wrapfigure}{r}{0.56\textwidth}
\definecolor{barblue}{RGB}{51,102,254}
\renewcommand\sfdefault{phv}
\renewcommand\mddefault{mc}
\renewcommand\bfdefault{bc}
\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize,
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\small\color{black!70},
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar{Specific Aim 1}{1}{6}\\
\ganttbar{Specific Aim 2}{1}{9}\\
\ganttbar{Specific Aim 3}{5}{12}\\
\ganttbar{Program management}{1}{12}\\
\end{ganttchart}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project.}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms
and computing.  Ryham has been working on mathematical modeling with a
strong analytical background. Young has been working on many areas of
computational fluid dynamics and applications to math biology for many
years.  Jiang has been working on integral equation methods, fast
algorithms, and their applications to computational electromagnetics and
fluid dynamics for many years. Their recent collaborative work on the
HAP model in two dimensions has provided a solid foundation on the
proposed research.

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in
Section~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently in person.  The
PIs will share software packages, paper sources, and references on a
common \textsf{Git} repository. The resulting software packages will be
posted on the \textsf{Github} software repository.

>>>>

\noindent
{\bf Bryan Quaife}: {\em NSF DMS-2012560, Erosion, Transport, and
Dispersion in Granular and Porous Media}, \$249,636,
08/01/2020--07/31/2023, PI. {\em Intellectual Merit:} The goal of this
research is to develop high-order numerical methods to
simulate hydrological processes including erosion.

\noindent
{\it Broader impacts:} 
A second-year PhD student (Jake Cherry) has been assigned to this
project. Since the funding just began, results have not yet
been published or presented.

@@

\begin{wrapfigure}{r}{0.56\textwidth}
\definecolor{barblue}{RGB}{51,102,254}
\renewcommand\sfdefault{phv}
\renewcommand\mddefault{mc}
\renewcommand\bfdefault{bc}
\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize,
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\small\color{black!70},
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar{Specific Aim 1}{1}{6}\\
\ganttbar{Specific Aim 2}{1}{9}\\
\ganttbar{Specific Aim 3}{5}{12}\\
\ganttbar{Program management}{1}{12}\\
\end{ganttchart}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project.}
  \todo[inline]{Need to update Gantt table}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms
and computing.  Ryham has been working on mathematical modeling with a
strong analytical background. Young has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. Quaife has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two dimensions has
provided a solid foundation on the proposed research.

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in
Section~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently on Zoom and in
person when possible. The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.
